M-M paper, morphological dependence, red sequence

### 2015-04-15 papers/MbhMsph/mm.tex
fanculo il workshop

\cite{grahamscott2013} and \cite{scott2013} presented double power-law linear regressions 

@@

\section{Data}
\label{sec:data}
Our galaxy sample (see Table \ref{tab:sample}) 
consists of 66 objects for which a dynamical measurement of the black hole mass had been reported in the literature 
\citep{grahamscott2013,rusli2013bhmassesDM} at the time we started this project, 
and for which we were able to obtain useful bulge parameters from $3.6\rm~\mu m$ \emph{Spitzer} satellite imagery. 
Bulge magnitudes were derived from our state-of-the-art galaxy decompositions, which take into account 
bulges, disks, spiral arms, bars, rings, haloes, extended or unresolved nuclear sources and partially depleted cores.
Kinematical information \citep{atlas3dIII-MNRAS,scott2014,arnold2014} was used 
to confirm the presence of rotationally supported components in most early-type galaxies, 
and to identify their extent (intermediate-scale, embedded disks or large-scale disks). 
\emph{Paper I} will present the dataset used here to investigate the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - M_{\rm *,sph}$ diagrams, 
give details about the data reduction process and the sophisticated galaxy modelling technique that we developed, 
discuss how we estimated the uncertainties on the bulge parameters, 
and illustrate the individual 66 galaxy decompositions. \\
Bulge luminosities\footnote{Absolute luminosities were calculated 
assuming a $3.6\rm~\mu m$ solar absolute magnitude of $3.25\rm~mag$ \citep{sani2011}.} 
were first converted into stellar masses using a constant $3.6\rm~\mu m$ mass-to-light ratio, $\Gamma_{3.6} = 0.6$ \citep{meidt2014}.
We then explored a more sophisticated way to compute mass-to-light ratios, 
using the color-$\Gamma_{3.6}$ relation published by 
\citeauthor{meidt2014} (\citeyear{meidt2014}, their equation 4), 
which allows one to estimate $\Gamma_{3.6}$ of a galaxy from its $[3.6] - [4.5]$ color. 
Individual $[3.6] - [4.5]$ colors\footnote{These are integrated $[3.6] - [4.5]$ colors, measured in a circular aperture 
within one galaxy's effective radius.} were taken from 
\citeauthor{peletier2012} (\citeyear{peletier2012}, column 8 of their Table 1) 
when available for our galaxies, 
or were estimated from the bulge stellar velocity dispersion, $\sigma$, 
using the color-$\sigma$ relation presented by \citeauthor{peletier2012} (\citeyear{peletier2012}, their Figure 6).
We found that the range in $[3.6] - [4.5]$ color is small ($0.06\rm~mag$), 
and thus the range in $\Gamma_{3.6}$ is also small ($0.04$).
After checking that using a single $\Gamma_{3.6} = 0.6$, independent of $[3.6] - [4.5]$ color, 
does not significantly affect the results of our analysis, 
we decided to use individual, color-dependent mass-to-light ratios. \\
The S\'ersic/core-S\'ersic classification presented in this work 
comes from the compilation of \citet{savorgnangraham2014},
who identified partially depleted cores according to the same criteria used by \citet{grahamscott2013}.
When no high-resolution image analysis was available from the literature, 
they inferred the presence of a partially depleted core based on the stellar velocity dispersion:
a galaxy is classified as core-S\'ersic if $\sigma > 270\rm~km~s^{-1}$,
or as S\'ersic if $\sigma < 166\rm~km~s^{-1}$. \\
For each galaxy, the total luminosity (or galaxy luminosity, $L_{\rm gal}$) is the sum of the luminosities of all its sub-components. 
Due to the complexity of their modelling, 
four galaxies (see Table \ref{tab:sample}, column 7) had their galaxy luminosities 
underestimated\footnote{These four cases will be discussed in \emph{Paper I}.}, 
which are given here as lower limits.

\input{table_sample.tex}

%\begin{figure}[h]
%\begin{center}
%\includegraphics[width=\columnwidth]{images/mag_lit_vs_mag_my.pdf}
%\caption{}
%\label{fig:}
%\end{center}
%\end{figure}

@@

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/mbh_vs_mag_tot.pdf}
\caption{Black hole mass against $3.6\rm~\mu m$ galaxy absolute magnitude. 
Symbols are coded as in Figure \ref{fig:mbhmagsph}.
Four spiral galaxies had their magnitudes overestimated and are shown as upper limits. 
}
\label{fig:}
\end{center}
\end{figure}

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/mbh_vs_mass_sph_agn.pdf}
\caption{Black hole mass against spheroid stellar mass. 
Symbols are coded as in Figure \ref{fig:mbhmagsph}, 
with the addition of the blue dots representing {\bf the AGN sample Jiang}, 
and the blue crossed circles denoting {\bf the other AGNs}.
The red dashed line indicates the BCES bisector linear regression for early-type galaxies (ellipticals+lenticulars), 
with the red shaded area denoting its $1\sigma$ uncertainty. 
The blue solid line shows the BCES bisector linear regression for spiral galaxies, 
with the blue shaded area denoting its $1\sigma$ uncertainty. }
\label{fig:mbhmasssph}
\end{center}
\end{figure}

@@

\begin{table*}
\centering
\caption{Linear regression analysis. {\bf X0 is the average X of the subsample...}}
\begin{tabular}{llccccc}
\hline
\hline
{\bf Subsample (size)} & {\bf Regression} & $\boldsymbol \alpha$ & $\boldsymbol \beta$ & $\boldsymbol X_0$ & $\boldsymbol \epsilon$ & $\boldsymbol \Delta$ \\ 
\hline 
\\
{\bf Spheroids} & \multicolumn{6}{l}{$\log[M_{\rm BH}/{\rm M_\odot}] = \alpha + \beta[(MAG_{\rm sph} - X_0)/{\rm mag}]$} \\ [0.5em]
All (66)	       & BCES OLS$(Y|X)$   & $8.16 \pm 0.07$ & $-0.44 \pm 0.04$ & $-23.86$ & $-$ & $0.56$ \\
		       & BCES OLS$(X|Y)$   & $8.16 \pm 0.08$ & $-0.61 \pm 0.05$ & $-23.86$ & $-$ & $0.68$ \\
		       & BCES Bisector     & $8.16 \pm 0.07$ & $-0.52 \pm 0.04$ & $-23.86$ & $-$ & $0.60$ \\
		       & mFITEXY OLS$(Y|X)$ & $8.17^{+0.07}_{-0.06}$ & $-0.43^{+0.03}_{-0.03}$ & $-23.86$ & $0.49$ & $0.56$ \\
		       & mFITEXY OLS$(X|Y)$ & $8.15^{+0.07}_{-0.07}$ & $-0.61^{+0.04}_{-0.05}$ & $-23.86$ & $0.96$ & $0.67$ \\
		       & mFITEXY Bisector   & $8.16^{+0.07}_{-0.07}$ & $-0.51^{+0.04}_{-0.04}$ & $-23.86$ & $-$    & $0.60$ \\

@@

%Ellipticals (E) (30)   & BCES OLS$(Y|X)$   & $8.80 \pm 0.07$ & $-0.53 \pm 0.09$ & $-25.45$ & $-$    & $0.42$ \\
% 		       & BCES OLS$(X|Y)$   & $8.80 \pm 0.08$ & $-0.66 \pm 0.07$ & $-25.45$ & $-$    & $0.48$ \\
% 		       & BCES Bisector     & $8.80 \pm 0.08$ & $-0.59 \pm 0.07$ & $-25.45$ & $-$    & $0.44$ \\
% 		       & FITEXY OLS$(Y|X)$ & $8.81^{+0.07}_{-0.07}$ & $-0.44^{+0.06}_{-0.07}$ & $-25.45$ & $0.33$     & $0.40$ \\
% 		       & FITEXY OLS$(X|Y)$ & $8.78^{+0.09}_{-0.09}$ & $-0.7^{+0.1}_{-0.1}$    & $-25.45$ & $0.60$     & $0.50$\\
% 		       & FITEXY Bisector   & $8.80^{+0.08}_{-0.08}$ & $-0.56^{+0.08}_{-0.10}$ & $-25.45$ & $-$        & $0.43$ \\
%
%Lenticulars (S0) (13)  & BCES OLS$(Y|X)$   & $7.9 \pm 0.1$ & $-0.4 \pm 0.2$ & $-22.19$ & $-$    & $0.56$ \\
% 		       & BCES OLS$(X|Y)$   & $7.9 \pm 0.3$ & $-1.1 \pm 0.5$ & $-22.19$ & $-$    & $1.01$ \\
% 		       & BCES Bisector     & $7.9 \pm 0.2$ & $-0.7 \pm 0.2$ & $-22.19$ & $-$    & $0.69$ \\
% 		       & FITEXY OLS$(Y|X)$ & $7.9^{+0.2}_{-0.1}$ & $-0.3^{+0.2}_{-0.2}$ & $-22.19$ & $0.51$     & $0.56$ \\
% 		       & FITEXY OLS$(X|Y)$ & $7.8^{+0.3}_{-0.4}$ & $-1.3^{+0.4}_{-1.3}$ & $-22.19$ & $0.71$     & $1.20$\\
% 		       & FITEXY Bisector   & $7.9^{+0.2}_{-0.3}$ & $-0.7^{+0.3}_{-0.4}$ & $-22.19$ & $-$        & $0.71$ \\
%
Early-type (E+S0) (45) & BCES OLS$(Y|X)$   & $8.56 \pm 0.07$ & $-0.33 \pm 0.04$ & $-24.47$ & $-$    & $0.46$ \\
 		       & BCES OLS$(X|Y)$   & $8.56 \pm 0.08$ & $-0.48 \pm 0.05$ & $-24.47$ & $-$    & $0.55$ \\
 		       & BCES Bisector     & $8.56 \pm 0.07$ & $-0.40 \pm 0.04$ & $-24.47$ & $-$    & $0.49$ \\
 		       & mFITEXY OLS$(Y|X)$ & $8.56^{+0.06}_{-0.06}$ & $-0.32^{+0.03}_{-0.04}$ & $-24.47$ & $0.40$ & $0.46$ \\
 		       & mFITEXY OLS$(X|Y)$ & $8.54^{+0.08}_{-0.08}$ & $-0.49^{+0.05}_{-0.06}$ & $-24.47$ & $1.00$ & $0.57$\\
 		       & mFITEXY Bisector   & $8.55^{+0.07}_{-0.07}$ & $-0.41^{+0.04}_{-0.05}$ & $-24.47$ & $-$    & $0.49$ \\

Late-type (S) (17) & BCES OLS$(Y|X)$   & $7.2 \pm 0.2$ & $-0.8 \pm 0.4$ & $-22.33$ & $-$    & $0.70$ \\
 		   & BCES OLS$(X|Y)$   & $7.2 \pm 0.3$ & $-1.7 \pm 0.7$ & $-22.33$ & $-$    & $1.26$ \\
 		   & BCES Bisector     & $7.2 \pm 0.2$ & $-1.1 \pm 0.3$ & $-22.33$ & $-$    & $0.88$ \\
 		   & mFITEXY OLS$(Y|X)$ & $7.2^{+0.1}_{-0.1}$ & $-0.5^{+0.2}_{-0.2}$ & $-22.33$ & $0.54$ & $0.63$ \\
 		   & mFITEXY OLS$(X|Y)$ & $7.4^{+0.5}_{-0.3}$ & $-2.0^{+0.7}_{-2.3}$ & $-22.33$ & $0.54$ & $1.51$ \\
 		   & mFITEXY Bisector   & $7.3^{+0.4}_{-0.3}$ & $-1.0^{+0.3}_{-0.5}$ & $-22.33$ & $-$    & $0.82$ \\
\hline 
\\
{\bf Total galaxies} & \multicolumn{6}{l}{$\log[M_{\rm BH}/{\rm M_\odot}] = \alpha + \beta[(MAG_{\rm gal} - X_0)/{\rm mag}]$} \\ [0.5em]
All (62)               & BCES OLS$(Y|X)$   & $8.26 \pm 0.08$ & $-0.49 \pm 0.06$ & $-24.78$ & $-$ & $0.64$ \\
 		       & BCES OLS$(X|Y)$   & $8.3 \pm 0.1$   & $-1.0 \pm 0.1$   & $-24.78$ & $-$ & $0.92$ \\
 		       & BCES Bisector     & $8.26 \pm 0.09$ & $-0.72 \pm 0.07$ & $-24.78$ & $-$ & $0.71$ \\
 		       & mFITEXY OLS$(Y|X)$ & $8.26^{+0.08}_{-0.08}$ & $-0.48^{+0.06}_{-0.07}$ & $-24.78$ & $0.62$ & $0.64$ \\
 		       & mFITEXY OLS$(X|Y)$ & $8.3^{+0.1}_{-0.1}$    & $-1.0^{+0.1}_{-0.2}$    & $-24.78$ & $0.87$ & $0.93$ \\
 		       & mFITEXY Bisector   & $8.3^{+0.1}_{-0.1}$    & $-0.72^{+0.08}_{-0.10}$ & $-24.78$ & $-$    & $0.71$ \\

@@

%All (62)		& BCES OLS$(Y|X)$   & $$ & $$ & $$ & $-$ & $$ \\
%			& BCES OLS$(X|Y)$   & $$ & $$ & $$ & $-$ & $$ \\
%			& BCES Bisector     & $$ & $$ & $$ & $-$ & $$ \\
%			& FITEXY OLS$(Y|X)$ & $$ & $$ & $$ & $$ & $$ \\
%			& FITEXY OLS$(X|Y)$ & $$ & $$ & $$ & $$ & $$ \\
%			& FITEXY Bisector   & $$ & $$ & $$ & $-$    & $$ \\

@@

\section{Analysis and results}
\label{sec:res}
We performed a linear regression analysis of the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - L_{\rm gal}$ diagrams 
using the BCES code from \cite{akritasbershady1996} 
and also the FITEXY routine \citep{press1992} 
modified by \cite{tremaine2002} to account for the intrinsic vertical scatter, $\epsilon$. 
Because the BCES routine {\bf AL: did you wanna write (correctly) this sentence for me please? 
can give biased results (wrong slope) when the scatter is comparable to the range of the data},
we checked that the best-fit parameters obtained with the BCES code were consistent with those output by the modified FITEXY code.
In Table \ref{tab:lreg} we report the BCES and modified FITEXY linear regressions for S\'ersic/core-S\'ersic 
galaxies and for different morphological types (elliptical/lenticular, spiral).

\subsection{Black hole mass -- spheroid luminosity}
We show the $M_{\rm BH} - L_{\rm sph}$ diagram in Figure \ref{fig:mbhmagsph}. 
S\'ersic and core-S\'ersic spheroids have slopes consistent with each other (within their $1\sigma$ uncertainties), 
in disagreement with the findings of \cite{grahamscott2013}. 
core galaxies have same slope
sersic gal have shallower slope
magnitudes of bulges are brighter for the high luminosity sersic galaxies (embedded disks confused with large scale ones)
and fainter for the low luminosity ones (more components in galaxies)

ELL and S0s separately have both slopes consistent with 1. 
they define a single sequence.
vertical scatter along the early type sequence is constant?
if 2 overmassive bhs removed, what happens?
In the M-M diagram, bulges of early type galaxies have a slope of $\sim$1, while bulges of spiral galaxies have a slope of 2-3.
Linear regressions that we provide are symmetrical (to be compared with theoretical expectations) and non-symmetrical (to be used to predict BH masses).
Contrary to a previous claim, the bulge luminosity appears to be a better indicator of the BH mass than the galaxy luminosity.

>>>>

\citeauthor{grahamscott2013} (\citeyear{grahamscott2013}, hereafter GS13) and \citeauthor{scott2013} (\citeyear{scott2013}, hereafter S+13) 
presented double power-law linear regressions 

@@

\section{Data}
\label{sec:data}
Our galaxy sample (see Table \ref{tab:sample}) 
consists of 66 objects for which a dynamical measurement of the black hole mass had been reported in the literature 
(GS13, \citealt{rusli2013bhmassesDM}) at the time we started this project, 
and for which we were able to obtain useful bulge parameters from $3.6\rm~\mu m$ \emph{Spitzer} satellite imagery. 
Bulge magnitudes were derived from our state-of-the-art galaxy decompositions, which take into account 
bulges, disks, spiral arms, bars, rings, haloes, extended or unresolved nuclear sources and partially depleted cores.
Kinematical information \citep{atlas3dIII-MNRAS,scott2014,arnold2014} was used 
to confirm the presence of rotationally supported components in most early-type galaxies, 
and to identify their extent (intermediate-scale, embedded disks or large-scale disks). 
\emph{Paper I} will present the dataset used here to investigate the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - M_{\rm *,sph}$ diagrams, 
give details about the data reduction process and the sophisticated galaxy modelling technique that we developed, 
discuss how we estimated the uncertainties on the bulge parameters, 
and illustrate the individual 66 galaxy decompositions. \\
Bulge luminosities\footnote{Absolute luminosities were calculated 
assuming a $3.6\rm~\mu m$ solar absolute magnitude of $3.25\rm~mag$ \citep{sani2011}.} 
were first converted into stellar masses using a constant $3.6\rm~\mu m$ mass-to-light ratio, $\Gamma_{3.6} = 0.6$ \citep{meidt2014}.
We then explored a more sophisticated way to compute mass-to-light ratios, 
using the color-$\Gamma_{3.6}$ relation published by 
\citeauthor{meidt2014} (\citeyear{meidt2014}, their equation 4), 
which allows one to estimate $\Gamma_{3.6}$ of a galaxy from its $[3.6] - [4.5]$ color. 
Individual $[3.6] - [4.5]$ colors\footnote{These are integrated $[3.6] - [4.5]$ colors, measured in a circular aperture 
within one galaxy's effective radius.} were taken from 
\citeauthor{peletier2012} (\citeyear{peletier2012}, column 8 of their Table 1) 
when available for our galaxies, 
or were estimated from the bulge stellar velocity dispersion, $\sigma$, 
using the color-$\sigma$ relation presented by \citeauthor{peletier2012} (\citeyear{peletier2012}, their Figure 6).
We found that the range in $[3.6] - [4.5]$ color is small ($0.06\rm~mag$), 
and thus the range in $\Gamma_{3.6}$ is also small ($0.04$).
After checking that using a single $\Gamma_{3.6} = 0.6$, independent of $[3.6] - [4.5]$ color, 
does not significantly affect the results of our analysis, 
we decided to use individual, color-dependent mass-to-light ratios. \\
The S\'ersic/core-S\'ersic classification presented in this work 
comes from the compilation of \citet{savorgnangraham2014},
who identified partially depleted cores according to the same criteria used by GS13.
When no high-resolution image analysis was available from the literature, 
they inferred the presence of a partially depleted core based on the stellar velocity dispersion:
a galaxy is classified as core-S\'ersic if $\sigma > 270\rm~km~s^{-1}$,
or as S\'ersic if $\sigma < 166\rm~km~s^{-1}$. \\
For each galaxy, the total luminosity (or galaxy luminosity, $L_{\rm gal}$) is the sum of the luminosities of all its sub-components. 
Due to the complexity of their modelling, 
four galaxies (see Table \ref{tab:sample}, column 7) had their galaxy luminosities 
underestimated\footnote{These four cases will be discussed in \emph{Paper I}.}, 
which are given here as lower limits.

%\input{table_sample.tex}

@@

@@

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/mbh_vs_mag_tot.pdf}
\caption{Black hole mass against $3.6\rm~\mu m$ galaxy absolute magnitude. 
Symbols are coded as in Figure \ref{fig:mbhmagsph}.
Four spiral galaxies had their magnitudes overestimated and are shown as upper limits. 
}
\label{fig:mbhmaggal}
\end{center}
\end{figure}

\begin{figure}[h]
\begin{center}
%\includegraphics[width=\columnwidth]{images/mbh_vs_mass_sph_agn.pdf}
\includegraphics[width=\columnwidth]{images/mbh_vs_mass_sph_galsymb_agn.pdf}
\caption{Black hole mass against spheroid stellar mass. 
The galaxies from our sample are shown with large symbols (red = E, orange = E/S0 and S0, blue = S0/Sp and Sp, black = merger).
The 139 small blue dots represent the low-mass AGN sample from \cite{jiang2011a}. 
The blue crossed circles denote 35 additional galaxies (see \citealt{grahamscott2015}, their Table 2), 
some of which might have had their bulge stellar masses overestimated.
The red dashed line indicates the BCES bisector linear regression for early-type galaxies (ellipticals+lenticulars), 
with the red shaded area denoting its $1\sigma$ uncertainty. 
The blue solid line shows the BCES bisector linear regression for spiral galaxies, 
with the blue shaded area denoting its $1\sigma$ uncertainty. }
\label{fig:mbhmasssph}
\end{center}
\end{figure}

\begin{table*}
\centering
\caption{Linear regression analysis. {\bf X0 is the average X of the subsample...}}
\begin{tabular}{llccccc}
\hline
\hline
{\bf Subsample (size)} & {\bf Regression} & $\boldsymbol \alpha$ & $\boldsymbol \beta$ & $\boldsymbol X_0$ & $\boldsymbol \epsilon$ & $\boldsymbol \Delta$ \\ 
\hline 
\\
 & \multicolumn{6}{l}{\emph{Black hole mass -- spheroid luminosity}} \\
 & \multicolumn{6}{l}{$\log[M_{\rm BH}/{\rm M_\odot}] = \alpha + \beta[(MAG_{\rm sph} - X_0)/{\rm mag}]$} \\ [0.5em]
All (66)	       & BCES OLS$(Y|X)$   & $8.16 \pm 0.07$ & $-0.44 \pm 0.04$ & $-23.86$ & $-$ & $0.56$ \\
		       & BCES OLS$(X|Y)$   & $8.16 \pm 0.08$ & $-0.61 \pm 0.05$ & $-23.86$ & $-$ & $0.68$ \\
		       & BCES Bisector     & $8.16 \pm 0.07$ & $-0.52 \pm 0.04$ & $-23.86$ & $-$ & $0.60$ \\
		       & mFITEXY OLS$(Y|X)$ & $8.17^{+0.07}_{-0.06}$ & $-0.43^{+0.03}_{-0.03}$ & $-23.86$ & $0.49$ & $0.56$ \\
		       & mFITEXY OLS$(X|Y)$ & $8.15^{+0.07}_{-0.07}$ & $-0.61^{+0.04}_{-0.05}$ & $-23.86$ & $0.96$ & $0.67$ \\
		       & mFITEXY Bisector   & $8.16^{+0.07}_{-0.07}$ & $-0.51^{+0.04}_{-0.04}$ & $-23.86$ & $-$    & $0.60$ \\

@@

%Ellipticals (E) (30)   & BCES OLS$(Y|X)$   & $8.80 \pm 0.07$ & $-0.53 \pm 0.09$ & $-25.45$ & $-$    & $0.42$ \\
% 		       & BCES OLS$(X|Y)$   & $8.80 \pm 0.08$ & $-0.66 \pm 0.07$ & $-25.45$ & $-$    & $0.48$ \\
% 		       & BCES Bisector     & $8.80 \pm 0.08$ & $-0.59 \pm 0.07$ & $-25.45$ & $-$    & $0.44$ \\
% 		       & FITEXY OLS$(Y|X)$ & $8.81^{+0.07}_{-0.07}$ & $-0.44^{+0.06}_{-0.07}$ & $-25.45$ & $0.33$     & $0.40$ \\
% 		       & FITEXY OLS$(X|Y)$ & $8.78^{+0.09}_{-0.09}$ & $-0.7^{+0.1}_{-0.1}$    & $-25.45$ & $0.60$     & $0.50$\\
% 		       & FITEXY Bisector   & $8.80^{+0.08}_{-0.08}$ & $-0.56^{+0.08}_{-0.10}$ & $-25.45$ & $-$        & $0.43$ \\
%
%Lenticulars (S0) (13)  & BCES OLS$(Y|X)$   & $7.9 \pm 0.1$ & $-0.4 \pm 0.2$ & $-22.19$ & $-$    & $0.56$ \\
% 		       & BCES OLS$(X|Y)$   & $7.9 \pm 0.3$ & $-1.1 \pm 0.5$ & $-22.19$ & $-$    & $1.01$ \\
% 		       & BCES Bisector     & $7.9 \pm 0.2$ & $-0.7 \pm 0.2$ & $-22.19$ & $-$    & $0.69$ \\
% 		       & FITEXY OLS$(Y|X)$ & $7.9^{+0.2}_{-0.1}$ & $-0.3^{+0.2}_{-0.2}$ & $-22.19$ & $0.51$     & $0.56$ \\
% 		       & FITEXY OLS$(X|Y)$ & $7.8^{+0.3}_{-0.4}$ & $-1.3^{+0.4}_{-1.3}$ & $-22.19$ & $0.71$     & $1.20$\\
% 		       & FITEXY Bisector   & $7.9^{+0.2}_{-0.3}$ & $-0.7^{+0.3}_{-0.4}$ & $-22.19$ & $-$        & $0.71$ \\
%
{\bf Early-type (E+S0)} (45) & BCES OLS$(Y|X)$    & $8.56 \pm 0.07$ & $-0.33 \pm 0.04$ & $-24.47$ & $-$    & $0.46$ \\
 		      	     & BCES OLS$(X|Y)$    & $8.56 \pm 0.08$ & $-0.48 \pm 0.05$ & $-24.47$ & $-$    & $0.55$ \\
 		      	     & {\bf BCES Bisector}& $\boldsymbol{8.56 \pm 0.07}$ & $\boldsymbol{-0.40 \pm 0.04}$ & $\boldsymbol{-24.47}$ & $-$    & $\boldsymbol{0.49}$ \\
 		      	     & mFITEXY OLS$(Y|X)$ & $8.56^{+0.06}_{-0.06}$ & $-0.32^{+0.03}_{-0.04}$ & $-24.47$ & $0.40$ & $0.46$ \\
 		      	     & mFITEXY OLS$(X|Y)$ & $8.54^{+0.08}_{-0.08}$ & $-0.49^{+0.05}_{-0.06}$ & $-24.47$ & $1.00$ & $0.57$\\
 		      	     & mFITEXY Bisector   & $8.55^{+0.07}_{-0.07}$ & $-0.41^{+0.04}_{-0.05}$ & $-24.47$ & $-$	 & $0.49$ \\

{\bf Late-type (Sp)} (17) & BCES OLS$(Y|X)$    & $7.2 \pm 0.2$ & $-0.8 \pm 0.4$ & $-22.33$ & $-$    & $0.70$ \\
 		   	  & BCES OLS$(X|Y)$    & $7.2 \pm 0.3$ & $-1.7 \pm 0.7$ & $-22.33$ & $-$    & $1.26$ \\
 		   	  & {\bf BCES Bisector}& $\boldsymbol{7.2 \pm 0.2}$ & $\boldsymbol{-1.1 \pm 0.3}$ & $\boldsymbol{-22.33}$ & $-$    & $\boldsymbol{0.88}$ \\
 		   	  & mFITEXY OLS$(Y|X)$ & $7.2^{+0.1}_{-0.1}$ & $-0.5^{+0.2}_{-0.2}$ & $-22.33$ & $0.54$ & $0.63$ \\
 		   	  & mFITEXY OLS$(X|Y)$ & $7.4^{+0.5}_{-0.3}$ & $-2.0^{+0.7}_{-2.3}$ & $-22.33$ & $0.54$ & $1.51$ \\
 		   	  & mFITEXY Bisector   & $7.3^{+0.4}_{-0.3}$ & $-1.0^{+0.3}_{-0.5}$ & $-22.33$ & $-$	& $0.82$ \\
\hline 
\\
 & \multicolumn{6}{l}{\emph{Black hole mass -- galaxy luminosity}} \\
  & \multicolumn{6}{l}{$\log[M_{\rm BH}/{\rm M_\odot}] = \alpha + \beta[(MAG_{\rm gal} - X_0)/{\rm mag}]$} \\ [0.5em]
All (62)               & BCES OLS$(Y|X)$   & $8.26 \pm 0.08$ & $-0.49 \pm 0.06$ & $-24.78$ & $-$ & $0.64$ \\
 		       & BCES OLS$(X|Y)$   & $8.3 \pm 0.1$   & $-1.0 \pm 0.1$   & $-24.78$ & $-$ & $0.92$ \\
 		       & BCES Bisector     & $8.26 \pm 0.09$ & $-0.72 \pm 0.07$ & $-24.78$ & $-$ & $0.71$ \\
 		       & mFITEXY OLS$(Y|X)$ & $8.26^{+0.08}_{-0.08}$ & $-0.48^{+0.06}_{-0.07}$ & $-24.78$ & $0.62$ & $0.64$ \\
 		       & mFITEXY OLS$(X|Y)$ & $8.3^{+0.1}_{-0.1}$    & $-1.0^{+0.1}_{-0.2}$    & $-24.78$ & $0.87$ & $0.93$ \\
 		       & mFITEXY Bisector   & $8.3^{+0.1}_{-0.1}$    & $-0.72^{+0.08}_{-0.10}$ & $-24.78$ & $-$    & $0.71$ \\

@@

%All (62)		& BCES OLS$(Y|X)$   & $$ & $$ & $$ & $-$ & $$ \\
%			& BCES OLS$(X|Y)$   & $$ & $$ & $$ & $-$ & $$ \\
%			& BCES Bisector     & $$ & $$ & $$ & $-$ & $$ \\
%			& FITEXY OLS$(Y|X)$ & $$ & $$ & $$ & $$ & $$ \\
%			& FITEXY OLS$(X|Y)$ & $$ & $$ & $$ & $$ & $$ \\
%			& FITEXY Bisector   & $$ & $$ & $$ & $-$    & $$ \\
\hline 
\\
 & \multicolumn{6}{l}{\emph{Black hole mass -- spheroid stellar mass}} \\
  & \multicolumn{6}{l}{$\log[M_{\rm BH}/{\rm M_\odot}] = \alpha + \beta \log[(M_{\rm *,sph} - X_0)/{\rm M_\odot}]$} \\ [0.5em]
{\bf Early-type (E+S0)} (45)  & BCES OLS$(Y|X)$    & $8.56 \pm 0.07$ & $0.8 \pm 0.1$ & $10.81$ & $-$ & $0.48$ \\
		      	      & BCES OLS$(X|Y)$    & $8.56 \pm 0.08$ & $1.3 \pm 0.1$ & $10.81$ & $-$ & $0.59$ \\
		      	      & {\bf BCES Bisector}& $\boldsymbol{8.56 \pm 0.07}$ & $\boldsymbol{1.0 \pm 0.1}$ & $\boldsymbol{10.81}$ & $-$ & $\boldsymbol{0.51}$ \\
		      	      & FITEXY OLS$(Y|X)$  & $$ & $$ & $10.81$ & $$ & $$ \\
		      	      & FITEXY OLS$(X|Y)$  & $$ & $$ & $10.81$ & $$ & $$ \\
		      	      & FITEXY Bisector    & $$ & $$ & $10.81$ & $-$    & $$ \\

{\bf Late-type (Sp)} (17)    & BCES OLS$(Y|X)$    & $7.2 \pm 0.2$ & $1.9 \pm 1.5$ & $10.05$ & $-$ & $0.74$ \\
		     	     & BCES OLS$(X|Y)$    & $7.2 \pm 0.4$ & $5.9 \pm 3.4$ & $10.05$ & $-$ & $1.70$ \\
		     	     & {\bf BCES Bisector}& $\boldsymbol{7.2 \pm 0.2}$ & $\boldsymbol{3.0 \pm 1.3}$ & $\boldsymbol{10.05}$ & $-$ & $\boldsymbol{0.94}$ \\
		     	     & FITEXY OLS$(Y|X)$  & $$ & $$ & $10.05$ & $$ & $$ \\
		     	     & FITEXY OLS$(X|Y)$  & $$ & $$ & $10.05$ & $$ & $$ \\
		     	     & FITEXY Bisector    & $$ & $$ & $10.05$ & $-$    & $$ \\

@@

\section{Analysis}
\label{sec:anal}
We performed a linear regression analysis of the $M_{\rm BH} - L_{\rm sph}$, $M_{\rm BH} - M_{\rm *,sph}$ and $M_{\rm BH} - L_{\rm gal}$ diagrams 
using the BCES code from \cite{akritasbershady1996} 
and also the FITEXY routine \citep{press1992} 
modified by \cite{tremaine2002} to account for the intrinsic vertical scatter, $\epsilon$. 
Because the BCES routine {\bf AL: did you wanna write (correctly) this sentence for me please? 
can give biased results (wrong slope) when the scatter is comparable to the range of the data},
we checked that the best-fit parameters obtained with the BCES code were consistent with those output by the modified FITEXY code.
In Table \ref{tab:lreg} we report the BCES and modified FITEXY linear regressions, both symmetrical and non-symmetrical, 
for S\'ersic/core-S\'ersic galaxies and for different galaxy morphological types (elliptical/lenticular, spiral).
Symmetrical regressions are meant to be compared with theoretical expectations, 
whereas non-symmetrical Ordinary Least Squares $(Y|X)$ regressions -- 
since they minimize the scatter in the vertical direction -- 
can be used to predict black hole masses.

\section{Results and discussion}
\label{sec:res}
